### 2013-05-06 doc/icml2013/algo.tex
Added comments from Percy
Minor caps changes and math changes
Updated sections adding a brief discussion after Theorem 1 and before the experiments

\section{Spectral Experts Algorithm}
\label{sec:algo}

@@

% Full algorithm
Now we are ready to state our full algorithm, which we call Spectral Experts
(\algorithmref{algo:spectral-experts}).
First, we perform three regressions to recover the compound parameters
$M_1$ \refeqn{y1},
$M_2$ \refeqn{y2}, and
$M_3$ \refeqn{y3}.
Since $M_2$ and $M_3$ both only have rank $k$,
we can use nuclear norm regularization
\cite{Tomioka2011,NegahbanWainwright2009}
to exploit this low-rank structure and improve our compound parameter estimates.
In the algorithm, the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$
are set to $\frac{c}{\sqrt{n}}$ for some constant $c$.
The resulting semidefinite program is a standard one which has received
much attention in recent years.
We use a rather simple proximal gradient-based approach,
in which the nuclear norm is handled in closed form by taking an SVD
and soft-thresholding the singular values \cite{donoho95soft,cai10soft}.

% Tensor factorization
Having estimated the compound parameters $M_2$ and $M_3$,
it remains to recover the original parameters $\theta$.
\citet{AnandkumarGeHsu2012} showed that for $M_2$ and $M_3$ of
the forms in \refeqn{Mp}, it is possible to efficiently accomplish this.
Specifically, we first compute a whitening matrix $W$ based on the SVD of $M_2$
and use that to construct a tensor $T = M_3(W, W, W)$ whose factors are orthogonal.
We can use the robust tensor power method to compute all the
eigenvalues and eigenvectors of $T$, from which it is easy to recover
the parameters $\pi$ and $\{\beta_h\}$.

@@

\begin{algorithm}[t]
  \caption{Spectral Experts}
  \label{algo:spectral-experts}
  \begin{algorithmic}[1]
    \INPUT Three independent datasets $\mathcal{D}_r = \{ (\xn{1}, \yn{1}), \cdots, (\xn{n}, \yn{n}) \}$ for $r = 1, 2, 3$;
    %regularization strengths $\lambda_n^{(2)} = \frac{c_2}{\sqrt{n}}$, $\lambda_n^{(3)} = \frac{c_3}{\sqrt{n}}$;
    regularization strengths $\lambda_n^{(2)}$, $\lambda_n^{(3)}$;
    observation noise variance $\sigma^2$.
    \OUTPUT Parameters $\hat\theta = (\hat \pi, [\hat \beta_1 \mid \cdots \mid \hat \beta_k])$.
    \STATE Estimate compound parameters $M_2, M_3$ using \textbf{low-rank regression}:
    \begin{align}
      &\hat M_1 = \arg\min_{M_1} \label{eqn:estimateM1} \\
      &\quad\quad\frac{1}{2n} \sum_{(x,y) \in \sD_1} (\innerp{M_1}{x} - y)^2, \nonumber \\
      &\hat M_2 = \arg\min_{M_2} \quad \lambda_n^{(2)} \|M_2\|_* + \label{eqn:estimateM2} \\
      &\quad\quad\frac{1}{2n} \sum_{(x,y) \in \sD_2} (\innerp{M_2}{x\tp{2}} + \sigma^2 - y^2)^2, \nonumber \\
      &\hat M_3 = \arg\min_{M_3} \quad \lambda_n^{(3)} \|M_3\|_* + \label{eqn:estimateM3} \\
      &\quad\quad\frac{1}{2n} \sum_{(x,y) \in \sD_3} (\innerp{M_3}{x\tp{3}} + 3 \sigma^2\innerp{\hat M_1}{x} - y^3)^2. \nonumber
    \end{align}
    \STATE Estimate the parameters $\theta = (\pi, B)$ using \textbf{tensor factorization}:
    \begin{enumerate}
      \item [(a)] Compute whitening matrix $\hat W \in \Re^{d \times k}$ (such that $\hat W^\top
      \hat M_2 \hat W = I$) using SVD.
      \item [(b)] Compute the eigenvalues $\{\hat a_h\}_{h=1}^k$
      and eigenvectors $\{\hat v_h\}_{h=1}^k$
      of the whitened tensor $\hat M_3(\hat W, \hat W, \hat W) \in \Re^{k \times k \times k}$
      by using the robust tensor power method.
    \item [(c)] Set parameter estimates $\hat\pi_h = \frac{1}{\hat a_h^2}$
    and $\hat\beta_h = (\hat W^{\top})^\dagger (\hat a_h \hat v_h)$.
    \end{enumerate}
  \end{algorithmic}
\end{algorithm}

>>>>

\section{Spectral Experts algorithm}
\label{sec:algo}

@@

\begin{algorithm}[t]
  \caption{Spectral Experts}
  \label{algo:spectral-experts}
  \begin{algorithmic}[1]
    \INPUT Three datasets $\mathcal{D}_r = \{ (\xn{1}, \yn{1}), \cdots, (\xn{n}, \yn{n}) \}$ for $r = 1, 2, 3$;
    %regularization strengths $\lambda_n^{(2)} = \frac{c_2}{\sqrt{n}}$, $\lambda_n^{(3)} = \frac{c_3}{\sqrt{n}}$;
    regularization strengths $\lambda_n^{(2)}$, $\lambda_n^{(3)}$;
    observation noise variance $\sigma^2$.
    \OUTPUT Parameters $\hat\theta = (\hat \pi, [\hat \beta_1 \mid \cdots \mid \hat \beta_k])$.
    \STATE Estimate compound parameters $M_2, M_3$ using \textbf{low-rank regression}:
    \begin{align}
      &\hat M_1 = \arg\min_{M_1} \label{eqn:estimateM1} \\
      &\quad\quad\frac{1}{2n} \sum_{(x,y) \in \sD_1} (\innerp{M_1}{x} - y)^2, \nonumber \\
      &\hat M_2 = \arg\min_{M_2} \quad \lambda_n^{(2)} \|M_2\|_* + \label{eqn:estimateM2} \\
      &\quad\quad\frac{1}{2n} \sum_{(x,y) \in \sD_2} (\innerp{M_2}{x\tp{2}} + \sigma^2 - y^2)^2, \nonumber \\
      &\hat M_3 = \arg\min_{M_3} \quad \lambda_n^{(3)} \|M_3\|_* + \label{eqn:estimateM3} \\
      &\quad\quad\frac{1}{2n} \sum_{(x,y) \in \sD_3} (\innerp{M_3}{x\tp{3}} + 3 \sigma^2\innerp{\hat M_1}{x} - y^3)^2. \nonumber
    \end{align}
    \STATE Estimate the parameters $\theta = (\pi, B)$ using \textbf{tensor factorization}:
    \begin{enumerate}
      \item [(a)] Compute whitening matrix $\hat W \in \Re^{d \times k}$ (such that $\hat W^\top
      \hat M_2 \hat W = I$) using SVD.
      \item [(b)] Compute the eigenvalues $\{\hat a_h\}_{h=1}^k$
      and eigenvectors $\{\hat v_h\}_{h=1}^k$
      of the whitened tensor $\hat M_3(\hat W, \hat W, \hat W) \in \Re^{k \times k \times k}$
      by using the robust tensor power method.
    \item [(c)] Set parameter estimates $\hat\pi_h = \frac{1}{\hat a_h^2}$
    and $\hat\beta_h = (\hat W^{\top})^\dagger (\hat a_h \hat v_h)$.
    \end{enumerate}
  \end{algorithmic}
\end{algorithm}

% Full algorithm
Now we are ready to state our full algorithm, which we call Spectral Experts
(\algorithmref{algo:spectral-experts}).
First, we perform three regressions to recover the compound parameters
$M_1$ \refeqn{y1},
$M_2$ \refeqn{y2}, and
$M_3$ \refeqn{y3}.
Since $M_2$ and $M_3$ both only have rank $k$,
we can use nuclear norm regularization
\cite{Tomioka2011,NegahbanWainwright2009}
to exploit this low-rank structure and improve our compound parameter estimates.
In the algorithm, the regularization strengths $\lambda_n^{(2)}$ and $\lambda_n^{(3)}$
are set to $\frac{c}{\sqrt{n}}$ for some constant $c$.
The resulting semidefinite program is a standard one which has received
much attention in recent years.
% We use a standard off-the-shelf SDP solver, CVX, to solve .
% We use a rather simple proximal gradient-based approach,
% in which the nuclear norm is handled in closed form by taking an SVD
% and soft-thresholding the singular values \cite{donoho95soft,cai10soft}.

% Tensor factorization
Having estimated the compound parameters $M_1$, $M_2$ and $M_3$, it
remains to recover the original parameters $\theta$.
\citet{AnandkumarGeHsu2012} showed that for $M_2$ and $M_3$ of
the forms in \refeqn{Mp}, it is possible to efficiently accomplish this.
Specifically, we first compute a whitening matrix $W$ based on the SVD of $M_2$
and use that to construct a tensor $T = M_3(W, W, W)$ whose factors are orthogonal.
We can use the robust tensor power method to compute all the
eigenvalues and eigenvectors of $T$, from which it is easy to recover
the parameters $\pi$ and $\{\beta_h\}$.

@@
